Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-06-16 paper/ms.tex
Update funding info
Update MW bar references

We have performed a simulation of a disk galaxy using the finite-volume
gravito-hydrodynamics code \AREPO{}.\cite{2010MNRAS.401..791S} In \AREPO{}, the
fluid is discretized as a moving Voronoi mesh. We use the additional physics
in the galaxy formation module Stars and MUltiphase Gas in GaLaxiEs (SMUGGLE)
\cite{2019MNRAS.489.4233M}. SMUGGLE is a comprehensive and self-consistent
galaxy formation model with a wide range of physical processes, including
radiative heating/cooling, star formation, and stellar feedback. More detailed
information on SMUGGLE is given in the Methods section. Our disk galaxy is a
modified version of the GALAKOS model\cite{2020ApJ...890..117D}, which
consists of a stellar disk, stellar bulge, and dark matter halo. After
$\sim2.5\,\textrm{Gyr}$ of evolution, the GALAKOS disk forms a bar consistent
with the Milky Way bar in terms of pattern speed and length
($\sim40\,\textrm{km}/\textrm{s}/\textrm{kpc}$ and $\sim4.5\,\textrm{kpc}$,
respectively). We modify this setup to include a gas phase, the details of
which are provided in the Methods section.

@@

\item [Acknowledgements] We would like to thank Greg~L. Bryan, Neal~J. Evans,
Drummond~B. Fielding, Keith Hawkins, Jason~A.~S. Hunt, Sarah~M.~R. Jeffreson,
Kathryn~V. Johnston, Peter~M.~W. Kalberla, Jürgen Kerp, Julio~F. Navarro,
Joshua~S. Speagle, Martin~D. Weinberg, and Yanfei Zou for helpful discussions.
A.B. would like to thank Todd Phillips for helpful discussions. Some
computations in this paper were run on the FASRC Cannon cluster supported by
the FAS Division of Science Research Computing Group at Harvard University.
Resources supporting this work were also provided by the NASA High-End
Computing (HEC) Program through the NASA Advanced Supercomputing (NAS)
Division at Ames Research Center. This research has made use of the Spanish
Virtual Observatory (https://svo.cab.inta-csic.es) project funded by
MCIN/AEI/10.13039/501100011033/ through grant PID2020-112949GB-I00. A.B. was
supported by the Future Investigators in NASA Earth and Space Science and
Technology (FINESST) award number 80NSSC20K1536 during the completion of this
work. L.H. funding. E.D. funding. C.C. funding. J.Q. acknowledges support from
NSF grant AST-2008490. L.V.S. is grateful for financial support from NASA ATP
80NSSC20K0566, NSF AST 1817233 and NSF CAREER 1945310 grants. P.T.
acknowledges support from NSF grant AST-1909933, AST-2008490, and NASA ATP
Grant 80NSSC20K0502. M.V. acknowledges support through NASA ATP 19-ATP19-0019,
19-ATP19-0020, 19-ATP19-0167, and NSF grants AST-1814053, AST-1814259,
AST-1909831, AST-2007355 and AST-2107724.

>>>>

We have performed a simulation of a disk galaxy using the finite-volume
gravito-hydrodynamics code \AREPO{}.\cite{2010MNRAS.401..791S} In \AREPO{},
the fluid is discretized as a moving Voronoi mesh. We use the additional
physics in the galaxy formation module Stars and MUltiphase Gas in GaLaxiEs
(SMUGGLE) \cite{2019MNRAS.489.4233M}. SMUGGLE is a comprehensive and
self-consistent galaxy formation model with a wide range of physical
processes, including radiative heating/cooling, star formation, and stellar
feedback. More detailed information on SMUGGLE is given in the Methods
section. Our disk galaxy is a modified version of the GALAKOS
model\cite{2020ApJ...890..117D}, which consists of a stellar disk, stellar
bulge, and dark matter halo. After $\sim2.5\,\textrm{Gyr}$ of evolution, the
GALAKOS disk forms a bar consistent with the Milky Way bar in terms of pattern
speed and length
($\sim40\,\textrm{km}/\textrm{s}/\textrm{kpc}$\cite{2022arXiv220606207G} and
$\sim4.5\,\textrm{kpc}$\cite{2015MNRAS.450.4050W}, respectively). We modify
this setup to include a gas phase, the details of which are provided in the
Methods section.

@@

\item [Acknowledgements] We would like to thank Greg~L. Bryan, Neal~J. Evans,
Drummond~B. Fielding, Keith Hawkins, Jason~A.~S. Hunt, Sarah~M.~R. Jeffreson,
Kathryn~V. Johnston, Peter~M.~W. Kalberla, Jürgen Kerp, Julio~F. Navarro,
Joshua~S. Speagle, Martin~D. Weinberg, and Yanfei Zou for helpful discussions.
A.B. would like to thank Todd Phillips for helpful discussions. Some
computations in this paper were run on the FASRC Cannon cluster supported by
the FAS Division of Science Research Computing Group at Harvard University.
Resources supporting this work were also provided by the NASA High-End
Computing (HEC) Program through the NASA Advanced Supercomputing (NAS)
Division at Ames Research Center. This research has made use of the Spanish
Virtual Observatory (https://svo.cab.inta-csic.es) project funded by
MCIN/AEI/10.13039/501100011033/ through grant PID2020-112949GB-I00. A.B. was
supported by the Future Investigators in NASA Earth and Space Science and
Technology (FINESST) award number 80NSSC20K1536 during the completion of this
work. E.D. was partially supported by HST grants HST-AR-16363.001 and
HST-AR-16602.006-A and by NASA Award NASA 80NSSC22K0761. J.Q. acknowledges
support from NSF grant AST-2008490. L.V.S. is grateful for financial support
from NASA ATP 80NSSC20K0566, NSF AST 1817233 and NSF CAREER 1945310 grants.
P.T. acknowledges support from NSF grant AST-1909933, AST-2008490, and NASA
ATP Grant 80NSSC20K0502. M.V. acknowledges support through NASA ATP
19-ATP19-0019, 19-ATP19-0020, 19-ATP19-0167, and NSF grants AST-1814053,
AST-1814259, AST-1909831, AST-2007355 and AST-2107724.
